\documentclass[10pt,a4paper]{article}

\usepackage{fontspec}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern} % serif, styl Computer Modern (Latin Modern)
\setmainfont{Times New Roman}
\usepackage[margin=1.6cm]{geometry}
\usepackage{hyperref}
\usepackage{microtype}
\usepackage[normalem]{ulem}
\hypersetup{
  colorlinks=true,
  urlcolor=black,
  linkcolor=black
}
\let\oldhref\href
\renewcommand{\href}[2]{\oldhref{#1}{\uline{#2}}}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{microtype}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=1.5em,itemsep=1pt,topsep=2pt,parsep=0pt}

% Section style matching Sachi Goyal: small caps, rule below
\titleformat{\section}
  {\large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{4pt}

\begin{document}

% ── Header ──────────────────────────────────────────────────────────────
\begin{center}
  {\huge \textbf{Marek Jóźwiak}}\\[4pt]
  \href{https://github.com/66HEX}{github.com/66HEX}
  \quad \textbullet \quad
  \href{https://www.madebyhex.com/}{madebyhex.com}
  \quad \textbullet \quad
  \href{https://www.linkedin.com/in/marek-j\%C3\%B3\%C5\%BAwiak-29958132a/}{linkedin.com/in/marek-jozwiak}
  \quad \textbullet \quad
  \href{mailto:hexthecoder@gmail.com}{hexthecoder@gmail.com}\\[2pt]
\end{center}

\vspace{2pt}
\noindent Self-taught frontend developer focused on immersive interfaces, real-time graphics, and reusable UI systems.
Builds production-ready web and desktop experiences with strong attention to performance and visual quality.

% ── Education ────────────────────────────────────────────────────────────
\section{Education}

\textbf{Zespół Szkół nr 9 im. Romualda Traugutta, Koszalin} \hfill Sep 2014 -- May 2018\\
\textit{Electronics Technician}

% ── Experience ───────────────────────────────────────────────────────────
\section{Experience}

\textbf{Creative Frontend Developer} $|$ \textit{Next.js, React, Three.js, GLSL, Tailwind CSS} \hfill Sep 2025 -- Dec 2025\\
\textit{shadcnblocks.com \textbar{} Contract \textbar{} Remote (Brisbane, Australia)}
\begin{itemize}
  \item Built 20 immersive, reusable full-screen React hero blocks for production use.
  \item Combined React Three Fiber, Three.js, and raw GLSL shaders to deliver real-time depth and motion.
  \item Delivered modular components compatible with shadcn/ui and Tailwind CSS.
\end{itemize}

\textbf{Partner} $|$ \textit{React, React Three Fiber, GLSL} \hfill Aug 2025 -- Dec 2025\\
\textit{21st.dev \textbar{} Contract \textbar{} Remote (Dover, Delaware, United States)}
\begin{itemize}
  \item Collaborated on reusable, production-ready React components for a community-driven UI registry.
  \item Designed component building blocks used by the MCP-powered generation workflow.
  \item Delivered modular components compatible with shadcn/ui and Tailwind CSS.
\end{itemize}

% ── Projects ─────────────────────────────────────────────────────────────
\section{Projects}

\textbf{Frame (Fast FFmpeg GUI)} $|$ \textit{Tauri v2, Rust, Svelte 5, TypeScript} \hfill\\
\href{https://github.com/66HEX/frame}{github.com/66HEX/frame} \textbar{} \href{https://www.framegui.app/}{framegui.app}
\begin{itemize}
  \item Built a high-performance media conversion app with concurrent queue management and real-time FFmpeg progress parsing.
  \item Added advanced codec/container workflows, presets, and hardware acceleration paths.
  \item Grew the project to 530+ stars on GitHub.
\end{itemize}

\textbf{Motion Core} $|$ \textit{Svelte 5, Three.js, GSAP} \hfill\\
\href{https://github.com/Motion-Core/motion-core}{github.com/Motion-Core/motion-core} \textbar{} \href{https://motion-core.dev/}{motion-core.dev}
\begin{itemize}
  \item Built a curated Svelte 5 motion component ecosystem for experimental UI.
  \item Worked on production-ready animation components powered by Three.js and GSAP.
  \item Supported a CLI-driven copy-paste component architecture for direct code ownership.
\end{itemize}

\textbf{Varsel} $|$ \textit{Svelte, TypeScript} \hfill\\
\href{https://github.com/66HEX/varsel}{github.com/66HEX/varsel}
\begin{itemize}
  \item Created a headless toast system for Svelte apps with status variants and promise helpers.
  \item Implemented position-aware stacks, swipe gestures, action callbacks, and lifecycle hooks.
  \item Maintained monorepo structure with publishable package and documentation site.
\end{itemize}

\textbf{SvelteKit Portfolio Template} $|$ \textit{SvelteKit 2, Svelte 5, Tailwind v4, Cloudflare Workers} \hfill\\
\href{https://github.com/66HEX/portfolio}{github.com/66HEX/portfolio} \textbar{} \href{https://www.madebyhex.com/}{madebyhex.com}
\begin{itemize}
  \item Built and maintained a production-oriented SvelteKit 2 portfolio template.
  \item Implemented markdown blog engine, SEO metadata flow, and Cloudflare Workers deployment path.
  \item Added backend routes for contact handling, anti-spam validation, and GitHub activity integration.
\end{itemize}

% ── Skills ───────────────────────────────────────────────────────────────
\section{Skills}

\textbf{Languages:} JavaScript, TypeScript, Rust, GLSL\\
\textbf{Frameworks:} Svelte, SvelteKit, React, Next.js\\
\textbf{3D and Motion:} Three.js, React Three Fiber, Threlte, GSAP\\
\textbf{Backend and Desktop:} Tauri, Node.js\\
\textbf{Cloud and Tools:} Cloudflare, AWS, Git, Figma, Tailwind CSS

% ── Certifications ────────────────────────────────────────────────────────
\section{Certifications}

\textbf{Programming S7-1200 Controllers in the TIA Portal Environment} \hfill Issued Jun 2017\\
Siemens

\textbf{AutoCAD Electrical} \hfill Issued Jun 2017\\
PROCAD SA

\textbf{AutoCAD Level I} \hfill Issued Jun 2017\\
PROCAD SA

\end{document}
